---
title: "Results dashboard | CliRSnow"
output: 
  flexdashboard::flex_dashboard:
    self_contained: false
    lib_dir: libs
    theme: bootstrap
    orientation: rows
    vertical_layout: fill
    social: menu
    source: embed
    logo: other/logo_72x48.png
    favicon: other/logo_72x48.png
    navbar:
      - { icon: "fa-share", title: "CliRSnow", href: "/", align: right }
---

```{r setup, include=FALSE}
library(flexdashboard)
library(leaflet)
```

```{r, include=TRUE}
htmltools::tagList(fontawesome::fa_html_dependency())
```

```{r meta, include=TRUE}
library(metathis)
meta() %>%
  meta_description(
    "Snow cover in the European Alps: Interactive dashboard with the main results from CliRSnow, an EU-funded research project."
  ) %>% 
  meta_viewport() %>% 
  meta_social(
    title = "Results dashboard | CliRSnow",
    url = "https://clirsnow.netlify.app/dash-results/",
    image = "https://clirsnow.netlify.app/dash-results/other/preview-main-dash.png",
    og_type = "website",
    og_author = c("Michael Matiu", "Peter J. Zellner"),
    twitter_card_type = "summary"
  )
```

## Row 1



### Stations

```{r}
valueBox(2149, icon = "fa-snowflake")
```

### Years of hi-res EO data

```{r}
valueBox(20, icon = "fas fa-satellite")
```

### Climate model simulations

```{r}
valueBox(27, icon = "fas fa-cloud-sun-rain")
```

### Future scenarios

```{r}
valueBox(2, icon = "fa-map-signs")
```


## Row 2


### Area of interest: The European Alps

```{r}
# leaflet() %>% 
#   addProviderTiles("Esri.NatGeoWorldMap") %>% 
#   fitBounds(4, 44, 18, 49)

sf_aoi <- data.frame(lon = c(4, 4, 19, 19),
           lat = c(43, 49, 49, 43)) %>% 
  sf::st_as_sf(coords = c("lon", "lat"),
           crs = 4326) %>% 
  dplyr::summarise(geometry = sf::st_combine(geometry)) %>%
  sf::st_cast("POLYGON")

leaflet(sf_aoi) %>%
  addProviderTiles("Esri.NatGeoWorldMap") %>% 
  addPolygons()

```

### Detailed results


#### How the topography of the Alps influences snow patterns


Statistical analysis of in-situ snow depth measurements and satellite observations.

<a href="./dash-climatology.html" class="btn btn-primary" role="button">Snow climatology</a>

<br>

#### How snow depth has changed in the past


Long-term trends in snow depth and related parameters from in-situ station observations.

<a href="./dash-past.html" class="btn btn-primary" role="button">Past trends 1971-2019</a>


<br>


#### How snow cover might change in the future


Future projections of snow cover fraction under different greenhouse gas concentration scenarios. 

<a href="./dash-future.html" class="btn btn-primary" role="button">Snow cover duration 2001-2100</a>


