---
title: "CLIRSNOW Past"
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    self_contained: true
    orientation: columns
    vertical_layout: fill
    social: ["menu"]
    logo: media/logo_72x48.png
    navbar:
      - { title: "CliRSnow", href: "/", align: right }
---


```{r setup, include=FALSE}
library(flexdashboard)

library(data.table)
library(magrittr)
library(lubridate)
library(ggplot2)
library(scico)
library(forcats)
library(plotly)
library(cluster)
library(foreach)
library(sf)
library(leaflet)
library(mapview)

cols_cluster <- setNames(scales::brewer_pal(palette = "Set1")(5),
                         c("NW", "NE", "North & high Alpine", "South & high Alpine", "SE"))
```



Regions {.storyboard}
=====================================

```{r data_regions, include=F}
load("/mnt/CEPH_PROJECTS/ALPINE_WIDE_SNOW/PAPER/02_review/rds/regions-01-sinkr-eof.rda")
dat_meta <- readRDS("/mnt/CEPH_PROJECTS/ALPINE_WIDE_SNOW/03_QC1/rds/1961-2020/meta_long_HN_HS.rds")
dat_meta_clust <- readRDS("/mnt/CEPH_PROJECTS/ALPINE_WIDE_SNOW/PAPER/02_review/rds/meta-with-cluster-01.rds")
mat_clust3_eof <- sinkr_eof$u

dat_regions <- foreach(
  kk = 2:5,
  .final = rbindlist
) %do% {

  km_fit <- kmeans(mat_clust3_eof[, 1:kk], kk)
  stn_clust <- km_fit$cluster
  data.table(kk = kk, 
             i_cluster = stn_clust,
             Name = colnames(mat_eof))
  
}

dat_plot_regions <- dat_regions %>% merge(dat_meta_clust, by = "Name")
dat_plot_regions[, Region := factor(i_cluster)]
dat_plot_regions[, label := paste0(
  Name, ", ", Elevation, "m, ", round(Longitude, 3), "°E ", round(Latitude, 3), "°N"
)]

sf_regions <- st_as_sf(dat_plot_regions,
                       coords = c("Longitude", "Latitude"),
                       crs = 4326)


```

```{r histalp_regions, include=FALSE}
histalp_reg_p = read_sf("R/17-dashboard_public/histalp_regions/Shape_CRSM_PR.shp")
histalp_reg_t = read_sf("R/17-dashboard_public/histalp_regions/Shape_CRSM_T.shp")

```



### 2 regions

```{r}
sf_cur <- sf_regions[sf_regions$kk == 2, ]
leaf_col <- colorFactor("Accent", levels(sf_cur$Region))
leaf_col_histalp = colorFactor("Accent", levels = histalp_reg_p$region)

# sf_cur %>% 
#   leaflet() %>% 
#   addProviderTiles("Esri.WorldTopoMap") %>% 
#   addCircleMarkers(color = ~leaf_col(Region),
#                    stroke = FALSE, 
#                    radius = 5,
#                    fillOpacity = 0.8,
#                    label = ~label)

mapview(sf_cur, zcol = "Region", label = "label", col.reg = leaf_col(sf_cur$Region), layer.name = "CliRSnow Regions") + 
  mapview(histalp_reg_p, zcol = "region", label = "region", 
          col.reg = leaf_col_histalp(histalp_reg_p$region), layer.name = "Histalp Precip.") + 
  mapview(histalp_reg_t, zcol = "region", label = "region", 
          col.reg = leaf_col_histalp(histalp_reg_t$region), layer.name = "Histalp Temp.")


```

***

Divides the whole Alps by elevation into high and low stations, irrespective of north-south or east-west orientation.

--> The main variability in snow is along elevation.

### 5 regions (used in study)


```{r}
sf_cur <- sf_regions[sf_regions$kk == 5, ]
leaf_col <- colorFactor("Set1", levels = levels(dat_meta_clust$cluster_fct))
leaf_col_histalp = colorFactor("Set1", levels = histalp_reg_p$region)

# sf_cur %>% 
#   leaflet() %>% 
#   addProviderTiles("Esri.WorldTopoMap") %>% 
#   addCircleMarkers(color = ~leaf_col(cluster_fct),
#                    stroke = FALSE, 
#                    radius = 5,
#                    fillOpacity = 0.8,
#                    label = ~label) 

mapview(sf_cur, zcol = "cluster_fct", label = "label", 
        col.reg = leaf_col(sf_cur$cluster_fct), layer.name = "CliRSnow Regions") + 
  mapview(histalp_reg_p, zcol = "region", label = "region", 
          col.reg = leaf_col_histalp(histalp_reg_p$region), layer.name = "Histalp Precip.") + 
  mapview(histalp_reg_t, zcol = "region", label = "region", 
          col.reg = leaf_col_histalp(histalp_reg_t$region), layer.name = "Histalp Temp.")




```


***

With 5 possible regions, the snow series in the Alps are divided by elevation, as well as gradients along north-south and east-west directions. These five regions were used in the analysis:

  - North & high Alpine
  - South & high Alpine
  - NW 
  - NE
  - SE

--> Elevation, the north-south divide, and the east-west gradient are the major drivers of snow variability. 

This results in a consistent picture with the Alpine climate, where snow mirrors the temperature and precipiation patterns in the Alps.


Trends by season 1971-2019 {.storyboard data-navmenu="Trends"}
=========================================

```{r data_trends, include=FALSE}

# set elevation interval -------------------------------------------------------
elev_int <- 500

# table start and end ----------------------------------------------------------
dat_meta_clust <- readRDS("/mnt/CEPH_PROJECTS/ALPINE_WIDE_SNOW/PAPER/02_review/rds/meta-with-cluster-01.rds")
dat_month <- readRDS("/mnt/CEPH_PROJECTS/ALPINE_WIDE_SNOW/PAPER/02_review/rds/data-01-monthly.rds")
dat_seasonal <- readRDS("/mnt/CEPH_PROJECTS/ALPINE_WIDE_SNOW/PAPER/02_review/rds/data-02-seasonal.rds")

# prep seasonal data -----------------------------------------------------------
dat_seasonal %>% 
  merge(dat_meta_clust, by = "Name") -> dat_plot_ts
dat_plot_ts[, elev_fct := cut(Elevation, breaks = seq(0, 3000, by = elev_int), dig.lab = 5)]
dat_plot_ts[, ns_fct := fct_collapse(cluster_fct,
                                     "North" = c("NE", "NW", "North & high Alpine"),
                                     "South" = c("South & high Alpine", "SE"))]


dat_plot_ts[, value_stn_mean := mean(value), .(Name, variable)]
dat_plot_ts[, value_anomaly := value - value_stn_mean]

dat_plot_ts_mean <- dat_plot_ts[, 
                                .(mean_value = mean(value),
                                  mean_value_anomaly = mean(value_anomaly),
                                  nn = .N),
                                .(year, variable, elev_fct, ns_fct)]


dat_plot_ts_mean[, year0 := year - min(year)]
dat_plot_ts_mean[nn > 5,
                 broom::tidy(lm(mean_value ~ year0)),
                 .(variable, elev_fct, ns_fct, nn)] %>% 
  dcast(variable + elev_fct + ns_fct + nn ~ term, value.var = "estimate") -> dat_table_start_end
setnames(dat_table_start_end, c("variable", "elevation", "region", "nn" ,"year1971", "trend"))

dat_table_start_end[, year2019 := year1971 + 49*trend]


# plot HS ----------------------------------------------------------------------
# prepare
# dat_plot <- dat_table_start_end[variable != "maxHS_NDJFMAM"]
dat_plot <- dat_table_start_end[startsWith(variable, "meanHS") & 
                                  !(variable %in% c("meanHS_MAM", "meanHS_NDJFMAM") & elevation == "(0,500]")]

dat_plot[, variable := fct_inorder(substr(variable, 8, 99))]
# dat_plot[, c("snow_index", "season") := tstrsplit(variable, "_")]

dat_plot[, rel_change := (year2019-year1971) / year1971]

dat_plot %>% 
  melt(measure.vars = c("year1971", "year2019"),
       variable.name = "year") -> dat_plot2
dat_plot2[, year := as.numeric(substr(year, 5, 9))]

dat_label_elev <- dat_plot2[year == 1971,
                            .(ypos = mean(value)),
                            .(year, variable, elevation)] 
dat_label_elev[, elevation_lbl := paste0(elevation, "m")]

dat_label_perc <- dat_plot2[year == 2019,
                            .(year, value, variable, elevation, region, rel_change)]
dat_label_perc[, lbl := scales::percent(rel_change, 1)]
dat_label_perc[, year := ifelse(region == "North", 2019, 2050)]

dat_label_perc_title <- dat_label_perc[, 
                                       .(value = max(value)),
                                       .(region, year)]
dat_label_perc_title[, value_max := max(value)]

# make the plot
# label number of stations
plot_trend_hs = dat_plot2 %>% 
  ggplot(aes(year, value, colour = region, linetype = elevation))+
  geom_point()+
  geom_line(aes(group = paste0(region, elevation)))+
  geom_text(data = dat_label_perc_title,
            aes(label = region, y = value_max, linetype = NULL),
            hjust = -0.2, vjust = -1)+
  geom_text(data = dat_label_perc,
            aes(label = lbl), hjust = -0.2)+
  geom_text(data = dat_label_elev,
            aes(y = ypos, colour = NULL, label = elevation_lbl), hjust = 1.1)+
  scale_x_continuous(limits = c(1900, 2100))+
  scale_color_brewer(palette = "Dark2")+
  facet_grid(. ~ variable)+
  theme_bw(14)+
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "none",
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank())+
  xlab("Change 1971-2019 (from linear trend)")+
  ylab("mean HS [cm]")


# plot SCD --------------------------------------------------------------------
# prepare
dat_plot <- dat_table_start_end[startsWith(variable, "SCD")]
# dat_plot <- dat_table_start_end[startsWith(variable, "meanHS") & 
                                  # !(variable %in% c("meanHS_MAM", "meanHS_NDJFMAM") & elevation == "(0,500]")]
dat_plot[, variable := factor(substr(variable, 5, 99),
                              levels = c("NDJF", "MAM", "NDJFMAM"))]
# dat_plot[, c("snow_index", "season") := tstrsplit(variable, "_")]

dat_plot[, rel_change := (year2019-year1971) / year1971]

dat_plot %>% 
  melt(measure.vars = c("year1971", "year2019"),
       variable.name = "year") -> dat_plot2
dat_plot2[, year := as.numeric(substr(year, 5, 9))]

dat_label_elev <- dat_plot2[year == 1971,
                            .(ypos = mean(value)),
                            .(year, variable, elevation)] 
dat_label_elev[, elevation_lbl := paste0(elevation, "m")]

dat_label_perc <- dat_plot2[year == 2019,
                            .(year, value, variable, elevation, region, rel_change)]
dat_label_perc[, lbl := scales::percent(rel_change, 1)]
dat_label_perc[, year := ifelse(region == "North", 2019, 2050)]

dat_label_perc_title <- dat_label_perc[, 
                                       .(value = max(value)),
                                       .(variable, region, year)]
dat_label_perc_title[, value_max := max(value), .(variable)]

# make the plot
# label number of stations
plot_trend_scd = dat_plot2 %>% 
  ggplot(aes(year, value, colour = region, linetype = elevation))+
  geom_point()+
  geom_line(aes(group = paste0(region, elevation)))+
  geom_text(data = dat_label_perc_title,
            aes(label = region, y = value_max, linetype = NULL),
            hjust = -0.2, vjust = -1)+
  geom_text(data = dat_label_perc,
            aes(label = lbl), hjust = -0.2)+
  geom_text(data = dat_label_elev,
            aes(y = ypos, colour = NULL, label = elevation_lbl), hjust = 1.1)+
  scale_x_continuous(limits = c(1900, 2100))+
  scale_color_brewer(palette = "Dark2")+
  facet_wrap( ~ variable, scales = "free_y")+
  theme_bw(14)+
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "none",
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank())+
  xlab("Change 1971-2019 (from linear trend)")+
  ylab("mean SCD [days]")

```



### Trend HS
```{r}
ggplotly(plot_trend_hs)

```


### Trend SCD
```{r}
ggplotly(plot_trend_scd)

```





